\bf Landslide: \\ Systematic Dynamic Race Detection in Kernel-space

### 2012-05-03 futurework.tex
add note about later transitions

>>>>

While studying various bugs found by Landslide, we found that in general, when there were frivolous thread switches in the decision trace, users most benefitted from starting to read the trace at the end; i.e., considering the most recent transition made by each thread. Hence, when building a search algorithm for trace minimisation, it would be good to more heavily prioritise decisions that occurred later in a buggy branch.
